---
title: "cops and schools"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(lubridate)
```

```{r}
classical_magnet <- read_csv("C:\\Users\\kates\\Downloads\\fixed_file.csv", skip=1) 
  
  
```

#Just cops. Find most common reasons for calls out.
```{r}

classical_magnet_law <- classical_magnet %>% 
  filter(`Agency Type` == "LAW") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))

  
```
most common is directed patrol, then juvenille complaint, then silent alarm


#Same but for EMS/FIRE
```{r}
classical_magnet_ems_fire <- classical_magnet %>% 
  filter(`Agency Type`=="FIRE"|`Agency Type`=="EMS") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```

#read in bulkeley(585 wethersfield and 395 lyme)
```{r}
bulkeley1 <- read_csv("C:\\Users\\kates\\Downloads\\copsinschools\\585wethersfield_fixed.csv",skip=1)

```
#just cops
```{r}
bulkeley1_law <- bulkeley1 %>% 
  filter(`Agency Type`=="LAW") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```

```{r}
bulkeley2 <- read_csv("C:\\Users\\kates\\Downloads\\395Lymefixed.csv")

bulkeley2_law <- bulkeley2 %>% 
  filter(`Agency Type`=="LAW") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```
#silent alarm is far and away most common at both addresses

```{r}
bulkeley1_ems_fire <- bulkeley1 %>% 
  filter(`Agency Type`=="FIRE"|`Agency Type`=="EMS") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```

```{r}
bulkeley2_ems_fire <- bulkeley2 %>% 
  filter(`Agency Type`=="FIRE"|`Agency Type`=="EMS") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```
#breathing difficulty, unconscious person, respectively


#Hartford Magnet
```{r}
hartford_magnet <- read_csv("C:\\Users\\kates\\Downloads\\53vernon.csv",skip=1)

hartford_magnet_law <- hartford_magnet %>% 
  filter(`Agency Type`=="LAW") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```
#silent alarm!

```{r}
hartford_magnet_ems_fire <- hartford_magnet %>% 
  filter(`Agency Type`=="FIRE"|`Agency Type`=="EMS") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```
#suicidal super high, group_by date to check how many actual. calling EMS =/ calling cops.

```{r}
kinsella <- read_csv("C:\\Users\\kates\\Downloads\\415granby.csv", skip=1)

kinsella_law <- kinsella %>% 
  filter(`Agency Type`=="LAW") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```
#directed patrol, silent alarm, community service

```{r}
kinsella_ems_fire <- kinsella %>% 
  filter(`Agency Type`== "FIRE"|`Agency Type`=="EMS") %>% 
  group_by(`Event Type`) %>% 
  summarise(count=n()) %>% 
  arrange(desc(count))
```
#alarm box, emotional disturb non-violent

